A meta-analysis of mental rotation ability in the first years of life

### 2022-04-12 code/analysis.Rmd
Add simulation for checking the MLM model

>>>>

```{r, simulation}
generate_exp <- function(id,
                         n_boys = 1e3,
                         n_girls = 1e3,
                         mean_diff_boys = 0,
                         mean_diff_girls = 2,
                         sd_diff_boys = 4,
                         sd_diff_girls = 4) {

  # Create randomly sampled data for boys and girls
  # Each element is the mean looking time difference for one infant
  boys <- rnorm(n_boys, mean_diff_boys, sd_diff_boys)
  girls <- rnorm(n_girls, mean_diff_girls, sd_diff_girls)

  # Compute separate effect sizes for the two split gender groups
  d_boys <- mean(boys) / sd(boys)
  d_girls <- mean(girls) / sd(girls)

  # Compute common effect size for the mixed gender group
  infants <- c(boys, girls)
  n_infants <- length(infants)
  d_infants <- mean(infants) / sd(infants)

  # Return all results for this experiment as a list
  return(list(
    id = id,
    n_boys = n_boys,
    n_girls = n_girls,
    n_infants = n_infants,
    d_boys = d_boys,
    d_girls = d_girls,
    d_infants = d_infants
  ))
}

# Generate random experiments
n_boys <- 1e3
n_girls <- 1e3
n_exps <- 100
ids <- paste0("exp_", 1:n_exps)
dat <- lapply(ids, generate_exp, n_boys, n_girls)
dat <- do.call(rbind.data.frame, dat)

### MIXED EXPERIMENTS ONLY ###

# Compute sampling variance of the effect size for each study; see
# https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/effects.html#w-group-smd
r_assumed <- .5
dat$v_d_infants <- with( # Sampling variances of the effect sizes
  dat, ((2 * (1 - r_assumed)) / n_infants) + (d_infants^2 / (2 * n_infants))
)

# Fit 3 level meta-analysis
res_full <- metafor::rma.mv(
  d_infants, v_d_infants,
  random = ~ id | id,
  data = dat,
  slab = id
)

# Check results
summary(res_full)
```
